---
title: "Default settings + in-memory"
output: 
    html_document: default
---

<style>
pre {
  overflow-x: auto;
}
pre code {
  word-wrap: normal;
  white-space: pre;
}
</style>

```{r global_options, echo = FALSE, include = FALSE}
options(width = 150)
```

Force reference purposes, make sure we're working with now outdated versions of *rhdf5* and *DelayedArray*

```{r, exhub, echo = FALSE, message = FALSE}
if(packageVersion('rhdf5') > "2.23.1") {
    BiocInstaller::biocLite('grimbough/rhdf5', ref = "6713b80", suppressUpdates = TRUE, ask = FALSE)
}
if(packageVersion('DelayedArray') > "0.5.6") {
    BiocInstaller::biocLite('Bioconductor/DelayedArray', ref = "82d7d8b", suppressUpdates = TRUE, ask = FALSE)
    BiocInstaller::biocLite("Bioconductor/HDF5Array", ref = "bd5760c", suppressUpdates = TRUE, ask = FALSE)
}
```
    
Loading the 10X brain data.
    
```{r, load-libs, message=FALSE}
library(TENxBrainData)
library(pryr)
library(microbenchmark)
```

```{r, load-data, message=FALSE}
tenx <- TENxBrainData()
dim(tenx)
```

```{r, select-subset}
tenx.sub <- tenx[,1:13000]
system.time(tenx.inmem <- as.matrix(counts(tenx.sub)))
object_size(tenx.sub)
object_size(tenx.inmem)
```

Calculating column sums for the on-disk version

```{r, save-results}
systime <- system.time(res1 <- colSums(counts(tenx.sub)))
save(res1, file = "res1.rda")
systime
```

Now we'll carry out the same calculation using the in-memory version.

```{r, save-results2}
systime.inmem <- system.time(res1a <- colSums(tenx.inmem))
save(res1a, file = "res1a.rda")
systime.inmem
```

Run both 5 more times to check consistency, and combined with the original results so we can load the all later.

```{r, step1-run-benchmark}
bm1 <- microbenchmark(colSums(counts(tenx.sub)),
                colSums(tenx.inmem), 
               times = 5L, unit = "s",
               control = list(order = "block", warmup = 0))

bm1 <- rbind(data.frame(expr = "", time = as.numeric(systime[3]) * 1e9), 
             bm1[1:5,],
             data.frame(expr = "", time = as.numeric(systime.inmem[3]) * 1e9),
             bm1[6:10,])

bm1$expr <- rep(c("naive", "in memory"), each = 6)
save(bm1, file = "bm1.rda")
bm1
```

```{r, sessionInfo}
devtools::session_info(c("HDF5Array", "DelayedArray"))
```



