---
title: "Uncompressed HDF5"
output: html_document
---

Here we use the default versions of **rhdf5** and **DelayedArray**, but with an uncompressed vesion of the counts table on disk.

```{r, setup, echo=FALSE, message=FALSE}

if(packageVersion('rhdf5') == "2.23.1.1") {
    BiocInstaller::biocLite('rhdf5', suppressUpdates = TRUE, ask = FALSE)
}
if(packageVersion('DelayedArray') == "0.5.1.1") {
    BiocInstaller::biocLite('DelayedArray', suppressUpdates = TRUE, ask = FALSE)
}
```

```{r, load-data, message=FALSE}
library(TENxBrainData)
library(microbenchmark)
tenx <- TENxBrainData()
options(DelayedArray.block.size=2e9)
```

The code below details how to create the HDF5 file containing the uncompressed dataset.  This requires being able to hold the entire matrix in memory (possibly twice due to internal R copying), so you need at least 300GB of RAM!

```{r, create-dataset, eval=FALSE}
library(rhdf5)
tenx.inmem <- as.matrix(counts(tenx))

h5File <- '/tmpdata/msmith/tenx_uncompressed.h5'
h5createFile(h5File)
h5createDataset(file = h5File, dataset = "counts", dims = dim(tenx.inmem), chunk = c(100,100),
                level = 0, storage.mode = "integer")
h5write(tenx.inmem, file = h5File, name = "counts" )
```

Now we create a new *SingleCellExperiment* object using the nncompressed HDF5Array as the counts table.

```{r, subset-data}
h5.uncmp <- HDF5Array(file = '/tmpdata/msmith/tenx_uncompressed.h5', 
                        name = "counts")
tenx.uncmp <- SingleCellExperiment(
    list(counts = h5.uncmp), rowData = rowData(tenx), colData = colData(tenx)
)
tenx.sub.uncmp <- tenx.uncmp[,1:130000]
```

Run first iteration and save the results.

```{r, save-results}
systime <- system.time(res2 <- colSums(counts(tenx.sub.uncmp)))
save(res2, file = "res2.rda")
systime
```

Benchmark 5 more times.

```{r, run-benchmark}
bm2 <- microbenchmark(colSums(counts(tenx.sub.uncmp)),
                      times = 5L, unit = "s",
                      control = list(order = "block", warmup = 0))
bm2 <- rbind(data.frame(expr = "", time = as.numeric(systime[3]) * 1e9), bm2)
bm2$expr <- "2GB block size2"
save(bm2, file = "bm2.rda")
bm2
```

```{r, sessionInfo}
sessionInfo()
```
